\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-11-07 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updated to figure 6 and 7 and the target z position

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target forms the detector central z-axis which is 
     along the beamline ; it is a 284~mm long, 6~mm diameter Kapton straw with 
     a 27~$\mu$m wall.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 $\mu$m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The average electric field in this region is perpendicular to the beam 
      and about 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}

>>>>

We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
starting from the beam line towards larger radius:\\
\begin{itemize}
  \item The 6~atm $^4$He target extends from -146~mm to 146~mm in z-direction 
     with respect to the center of the detector forming the detector central 
     axis. It is a 6~mm diameter Kapton straw with a 27~$\mu$m wall.
   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
      M\o{}ller electrons scattered by the beam. This region is surrounded by 
      a 4 $\mu$m thick window made of grounded aluminized Mylar.
   \item The second gas gap region extends between 20~mm and 30~mm and is 
      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
      aluminized Mylar set at $-4260$~V to serve as the cathode.
   \item The drift region is filled with the same Ne-DME gas mixture and 
      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
      The average electric field in this region is perpendicular to the beam 
      and about 550~V/cm.
   \item The electron amplification system is composed of three GEMs located at 
      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
      serves as the anode and each subsequent GEM is set at a lower voltage to
      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
      275~V bias is applied across each GEM for amplification.
   \item The readout board has an internal radius of 69~mm and collects charges 
      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
      directly on its outer side and transmit the signal to the data 
      acquisition electronics.
\end{itemize}

### 2017-11-07 eg6-letters/NIM/review-1/review-1.tex
more updated to figure 6 and 7 and the target z position

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{- The target tube is the central z-axis of the detector. The 
text is modified to make it clean.\\}
\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}

@@

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{blue}{This is a schematic to illustrate the definitions of 
   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
needed.}

>>>>

\item Relevant length and thicknesses of the various elements are reported in 
   the text and in the figure, can you please add also the z position of the 
   target w.r.t the detector? To give the complete information, I would also 
   add the value of the induction gap electric field, which is the only missing 
   field value and the value of the reached amplification gain with the three 
   GEM.\\
\textcolor{blue}{ The text has been modified to clarify the z position of the 
target with respect to the detector.\\}
\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
anyone know our exact field in this gap?\\}
\textcolor{blue}{- The gain of such GEM configuration has been studied by 
   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
one should not simply add gains to each other for multilayer GEM 
amplifications.  We did not evaluate precisely the overall gain in our chamber, 
so we do not have a value for our RTPC GEM system at this point.}

@@

\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
   extremities?\\
   \textcolor{blue}{The figure is updated.}
